method

### 2022-02-09 06_Paper/ER-ED/method.Rmd
added effect size to ratings

library(targets)    # to keep track of all relevant files
library(readxl)     # import excel files
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output
library(afex)       # for ANOVA
library(emmeans)
library(ggplot2)    # for nice plots
library(dplyr)
library(BayesFactor)

@@

@@

# figure
FigPilot1=ggplot2::ggplot(arousal_view, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neu", "view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

SubjArousalReg_aov <- afex::aov_ez(data = arousal_reg,
                              id = "ID",
                              dv = "arousal",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)

@@

@@

# figure
FigPilot2 = ggplot2::ggplot(arousal_reg, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

>>>>

library(targets)    # to keep track of all relevant files
library(readxl)     # import excel files
library(here)       # to set directories without defined paths
library(papaja)     # APA conform output
library(afex)       # for ANOVA
library(emmeans)
library(ggplot2)    # for nice plots
library(dplyr)
library(BayesFactor)
library(effectsize)

@@

SubjArousalView_con$etasq <- format(effectsize::t_to_eta2(t = SubjArousalView_con$t.ratio,
                                                          df_error = SubjArousalView_con$df,
                                                          ci = 0.95,
                                                          digits = 2))

@@

# figure
FigPilot1=ggplot2::ggplot(Ratings_view, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neu", "view_neg"),
                   labels = c("Neutral", "Negative"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")

@@

SubjArousalReg_aov <- afex::aov_ez(data = Ratings_reg,
                              id = "ID",
                              dv = "arousal",
                              within = "block",
                              fun_aggregate = mean,
                              include_aov = TRUE)

@@

SubjArousalReg_con$etasq <- format(effectsize::t_to_eta2(t = SubjArousalReg_con$t.ratio, df_error = SubjArousalReg_con$df, ci = 0.95), digits = 2)

@@

# figure
FigPilot2 = ggplot2::ggplot(Ratings_reg, aes(x = block, y = arousal))+
  geom_boxplot(width = 0.7, position = position_dodge(0.8))+
  scale_x_discrete(name = "Strategy", 
                   limits = c("view_neg", "distraction", "distancing", "suppression"),
                   labels = c("View", "Distraction", "Distancing", "Suppression"))+
  geom_jitter(size = 0.4)+
  labs(y = "Arousal Rating")
